

%Go to new page in latex
\newpage

\cvsection{Publications}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvhonor
    {Engineering a Digital Twin for Diagnosis and Treatment of Multiple Sclerosis}
    {D'Aloisio, G., Di Matteo, A., Cipriani, A., Lozzi, D., Mattei, E., Zanfardino, G., Di Marco, A., Placidi, G.}
    {ACM/IEEE MODELS 2024, pp. 364–369}
    {2024}

\cvhonor
  {A crowd simulation-based tool for environmentally hazard-conscious urban design}
  {Eugeni, F., Zanfardino, G., Di Ludovico, D.}
  {BDC. Bollettino Del Centro Calza Bini, 24(2), 147–162}
  {2024}

\cvhonor
  {Simulating crowd behaviour to implement safety-based urban design techniques aimed at optimizing evacuation}
  {Di Ludovico, D., Eugeni, F., Zanfardino, G., Di Marco, A.}
  {Journal of Urban Design, pp. 1–22}
  {2025}

\cvhonor
  {Coupling Exploratory Data Analysis and mL-Ops}
  {Zanfardino, G.}
  {Video Memorie della Societa Astronomica Italiana, 4, 22}
  {2023}

\cvhonor
  {Real-time FPM reconstruction and misalignment correction by numerical Multi-Look and GAN}
  {Bianco, V., Delli Priscoli, M., Valentino, M., Pirone, D., Behal, J., Zanfardino, G., et al.}
  {Computational Optical Sensing and Imaging, pp. CTh3C–4}
  {2022}

\cvhonor
  {Deep learning-based, misalignment resilient, real-time Fourier Ptychographic Microscopy reconstruction of biological tissue slides}
  {Bianco, V., Delli Priscoli, M., Pirone, D., Zanfardino, G., et al.}
  {IEEE Journal of Selected Topics in Quantum Electronics, 28(4)}
  {2022}
  
\cvhonor
  {ARDNA: A Mobile App Based on Augmented Reality for Supporting Knowledge Exploration in Learning Scenarios}
  {Genovese, A., Marino, F., Orciuoli, F., Zanfardino, G.}
  {Intelligent Tutoring Systems (ITS 2021), pp. 505–511}
  {2021}

\cvhonor
  {Unmask inflated product reviews through Machine Learning}
  {Bangerter, M. L., Fenza, G., Gallo, M., Genovese, A., Nota, F. D., Stanzione, C., Zanfardino, G.}
  {IEEE CIVEMSA 2021, pp. 1–6}
  {2021}

\cvhonor
  {Urban Digital Twin for Territorial Management}
  {Zanfardino, G.}
  {Discovery Science 2024}
  {2024}


\nocite{*}
\bibliographystyle{plain}
\bibliography{../publications}
